---
title: "BeckCourseProjectPhase1"
output: word_document
date: "2026-07-15"
---
#Course Project Phase 1 Data#

##Libraries##
```{r}
library(tidyverse)
library(tidymodels)
library(VIM)
library(mice)
library(naniar)
library(skimr)
library(ggplot2)
library(gridExtra)
```

##The Data Sets##

```{r}
sampledata = read_csv("sample_submission.csv")
train = read_csv("train.csv")
test = read_csv("test.csv")
```

##Missing Data Check##
###Sample Data###

```{r}
gg_miss_var(sampledata)
```
###Train Data###
```{r}
gg_miss_var(train)
```

###Test Data###
```{r}
gg_miss_var(test)
```
##Training Data Visualization##
### Conversion###
```{r}
train = train %>% mutate(failure = factor(failure))
```
###Attribute Comparison Visualization###
```{r}
p1 = ggplot(train, aes(x = attribute_2, fill = failure)) + geom_bar(position = "fill")
p2 = ggplot(train, aes(x = attribute_3, fill = failure)) + geom_bar(position = "fill")
grid.arrange(p1,p2)
```
###Measurements 0-3 Data Visualization###
```{r}
p3 = ggplot(train, aes(x = measurement_0, fill = failure)) + geom_bar(position = "fill")
p4 = ggplot(train, aes(x = measurement_1, fill = failure)) + geom_bar(position = "fill")
p5 = ggplot(train, aes(x = measurement_2, fill = failure)) + geom_bar(position = "fill")
p6 = ggplot(train, aes(x = measurement_3, fill = failure)) + geom_bar(position = "fill")
grid.arrange(p3,p4,p5,p6)
```
###Measurements 4-7 Data Visualization###
```{r}
p7 = ggplot(train, aes(x = measurement_4, fill = failure)) + geom_bar(position = "fill")
p8 = ggplot(train, aes(x = measurement_5, fill = failure)) + geom_bar(position = "fill")
p9 = ggplot(train, aes(x = measurement_6, fill = failure)) + geom_bar(position = "fill")
p10 = ggplot(train, aes(x = measurement_7, fill = failure)) + geom_bar(position = "fill")
grid.arrange(p7,p8,p9,p10)
```
###Measurements 8-11 Data Visualization###
```{r}
p11 = ggplot(train, aes(x = measurement_8, fill = failure)) + geom_bar(position = "fill")
p12 = ggplot(train, aes(x = measurement_9, fill = failure)) + geom_bar(position = "fill")
p13 = ggplot(train, aes(x = measurement_10, fill = failure)) + geom_bar(position = "fill")
p14 = ggplot(train, aes(x = measurement_11, fill = failure)) + geom_bar(position = "fill")
grid.arrange(p11,p12,p13,p14)
```
###Measurements 12-15 Data Visualization###
```{r}
p15 = ggplot(train, aes(x = measurement_12, fill = failure)) + geom_bar(position = "fill")
p16 = ggplot(train, aes(x = measurement_13, fill = failure)) + geom_bar(position = "fill")
p17 = ggplot(train, aes(x = measurement_14, fill = failure)) + geom_bar(position = "fill")
p18 = ggplot(train, aes(x = measurement_15, fill = failure)) + geom_bar(position = "fill")
grid.arrange(p15,p16,p17,p18)
```
###Measurements 16 And 17 Data Visualization###
```{r}
p19 = ggplot(train, aes(x = measurement_16, fill = failure)) + geom_bar(position = "fill")
p20 = ggplot(train, aes(x = measurement_17, fill = failure)) + geom_bar(position = "fill")
grid.arrange(p19,p20)
```



